---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Workspace


**Just do your best to complete all the exercises**

1. What is your current working directory?

```{r current-working-directory, exercise=TRUE}

```

2. Set your working directory 

```{r setting-working-directory, exercise= TRUE}

```

3. List all the loaded packages

```{r search-path, exercise = TRUE}

```

4. list all the objects available in your workspace

```{r all-objects, exercise=TRUE}

```
5. Check wheather `readr`, `readxl` and `haven` packages are installed, if not
  install them

```{r auto-install-packages, exercise = TRUE}

```

6. Check weather the `MASS` package is installed, then **get the help of it**

```{r mass-pkg, exercise = TRUE}

```

7. List all the data sets from `datasets` package.
 
```{r exploring-datasets, exercise = TRUE}

```

8. Load **three datasets** of your choice from the `datasets` package, and use 
`str()` function to check them

```{r loading-datasets, exercise = TRUE}

```

9. List the datasets from the `MASS` package, and from `carData` if installed 

```{r mass-and-carDara1, exercise = TRUE}

```
10. Load **three datasets** from each package (MASS and carData), and check the 
first few observations using the function `head()`

```{r mass-and-carDara2, exercise = TRUE}

```

## The Help is Your Friend
  **Please read the help of some very common functions I chose for you** 
  
1. Get the **help** of the function `help`

```{r help-help, exercise = TRUE}

```

2. Get the **help** of the function `ls()`

```{r help-ls, exercise = TRUE}

```

3. Get the **help** of the function `str()` 

```{r help-str, exercise = TRUE}

```

4. Get the **help** of the function `head()`

```{r help-head, exercise = TRUE}

```

5. Get the **help** of the function `vector()`, 

```{r help-vector, exercise = TRUE}

```

6. Get the **help** of the function `list()`

```{r help-list, exercise= TRUE}

```

7. Get the **help** of the function `data.frame`

```{r help-data-frame, exercise = TRUE}

```

8. Get the **help** of the function `factor`

```{r help-factor, exercise = TRUE}

```

9. Get the **help** of the function `seq`

```{r help-seq, exercise = TRUE}

```
10. Get the **help** of the function `matrix`

```{r help-matrix, exercise = TRUE}

```

11. Get the **help** of the function `rep`

```{r help-rep, exercise = TRUE}

```

12. Use the `example` function of `rep`, `list` and `seq`

```{r examples, exercise = TRUE}

```


## Quiz


  "The Next questions are TRUE, FALSE":

```{r quiz}
quiz(
  
  question("We can clean up by using rm(list=ls())?",
    answer("true",correct=TRUE),
    answer("false"),
        allow_retry = TRUE,
        correct = "Great!"
  ),
    question("help.start(),Is it taking you to the start page?",
    answer("true",correct=TRUE),
    answer("false"),
        allow_retry = TRUE,
        correct = "Great Job again!"
  ),
   question("We can list all the R objects by applying the str() function?",
    answer("true"),
    answer("false",correct=TRUE,),
        allow_retry = TRUE,
        correct = "Wonderful! Keep going"
  ),
     question("If you use the same dataset more often, you can use the attach() method?",
    answer("true",correct=TRUE),
    answer("false",),
        allow_retry = TRUE,
        correct = "See! you a hero!!!"
  ),
  question("If you need help, you put $ before the subject you want to know ?",
    answer("true"),
    answer("false",correct=TRUE),
        allow_retry = TRUE,
        correct = "Excellent!"
  ), 
  question("To get the path of the current working dictionary, you use ",
    answer("getwd()",correct=TRUE),
    answer("setwd()"),
        allow_retry = TRUE,
    correct="Great"
  ),  
    question("x=seq(1,10,length.out=5) , x=  ",
    answer("1 2 3 4 5 "),
    answer("1 3.25 5.50 7.75 10 ",correct=TRUE,),
    answer("1 2.5 5 7.5 10"),
        allow_retry = TRUE,

    correct = "I am proud of you"
    ),  
    question("An excel file extension is xlsx or xls?",
    answer("true",correct=TRUE),
    answer("false"),
    allow_retry = TRUE,
        correct = "You are about to make it!"


  ),
    question("R functionality is divided into a number of ?  ",
    answer("Packages",correct=TRUE),
    answer("Functions"),
    answer("Libraries"),
        allow_retry = TRUE,

    correct = "Great"
    ),
   question("What would be the output of the following code options=(digits=3) when excute print(1/3)?   ",
    answer("0.333",correct=TRUE),
    answer("0.333333"),
    answer("0.3"),
        allow_retry = TRUE,
    correct = "Great"
    ),
     question("     Output of the following code  z <- 0:3 z = ?   ",
    answer("0 3"),
    answer("0 1 2 3",correct=TRUE ),
    answer("0 1 2"),
        allow_retry = TRUE,
    correct = "That is great!, careful R is different than python if you made
    it from that language, The stop is not inclusive in python"
    )
  
)
```

